meta-analysis

### 2017-06-06 Code/4_combined-meta-regression.Rmd
made paths relativ

In the paper, we perform a random-effects meta regression, that includes random intercepts for each state and plot the general pattern (when the RE estimate is equal to 0). In this file we also include code for the fixed effect estimation, for interested readers. This model directly estimates vertical shifts to the mean curve for each state, which may be of interest to some readers.

```{r initialize, warning=F, message=F}
library(lme4)
library(splines)
library(broom)
library(tidyverse)

source("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Code/life_expectancy_functions.R")
```

```{r load-data}
cod_decomp_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/cod_decomp_results.csv")
cod_decomp_results$COD_cont_yrs_width <- cod_decomp_results$COD_cont_yrs_ucl - cod_decomp_results$COD_cont_yrs_lcl
cod_decomp_results$COD_cont_yrs_SE <- (cod_decomp_results$COD_cont_yrs_ucl - cod_decomp_results$COD_cont_yrs_lcl)/3.92

age_cod_results_female <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/age_cod_results_female.csv")
age_cod_results_male <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/age_cod_results_male.csv")
age_cod_results <- rbind(age_cod_results_female, age_cod_results_male)
rm(age_cod_results_female, age_cod_results_male)

age_cod_results$age_COD_cont_yrs_SE <- (age_cod_results$age_COD_cont_yrs_ucl - age_cod_results$age_COD_cont_yrs_lcl)/3.92
age_cod_results_infants_AOC <- subset(age_cod_results, age_minbin == 0 & COD == "All other causes")
```

```{r RE_meta_regression_of_cod_contribution, echo = F}
#Random effects meta analysis (fixed effects for state)

@@

```{r save_data}
write.csv(cod_decomp_results, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/cod_decomp_results.csv")

write.csv(age_cod_results_infants_AOC, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/age_cod_results_infants_AOC.csv")
```

>>>>

In the working paper, we perform a random-effects meta regression, that includes random intercepts for each state and plot the general pattern (when the RE estimate is equal to 0). In this file we also include code for the fixed effect estimation, for interested readers. This model directly estimates vertical shifts to the mean curve for each state, which may be of interest.

```{r initialize, warning=F, message=F}
library(lme4) #for random effects models
library(splines)
library(broom)
library(tidyverse)

source("./Code/life_expectancy_functions.R")
```

```{r load-data}
cod_decomp_results <- read.csv("./Results2/cod_decomp_results.csv")
cod_decomp_results$COD_cont_yrs_width <- cod_decomp_results$COD_cont_yrs_ucl - cod_decomp_results$COD_cont_yrs_lcl
cod_decomp_results$COD_cont_yrs_SE <- (cod_decomp_results$COD_cont_yrs_ucl - cod_decomp_results$COD_cont_yrs_lcl)/3.92

age_cod_results_female <- read.csv("./Results2/age_cod_results_female.csv")
age_cod_results_male <- read.csv("./Results2/age_cod_results_male.csv")
age_cod_results <- rbind(age_cod_results_female, age_cod_results_male)
rm(age_cod_results_female, age_cod_results_male)

age_cod_results$age_COD_cont_yrs_SE <- (age_cod_results$age_COD_cont_yrs_ucl - age_cod_results$age_COD_cont_yrs_lcl)/3.92

#the following is for our sensitivity analysis when we look only at infants and consider only the cause that 
#captures "all other causes" (since this is the most common cause for this age group).
age_cod_results_infants_AOC <- subset(age_cod_results, age_minbin == 0 & COD == "All other causes")
```

```{r RE_meta_regression_of_cod_contribution, echo = F}
#Random effects meta analysis (random intercepts for state)

@@

```{r save_data}
write.csv(cod_decomp_results, "./Results2/cod_decomp_results.csv")

write.csv(age_cod_results_infants_AOC, "./Results2/age_cod_results_infants_AOC.csv")
```
